Negative Types

### 2015-03-22 Univalence/outline.tex
outline
small cleanups

\paragraph*{DivModUtils.} External library for reasoning about uniqueness of \texttt{divMod}.

@@

\paragraph*{SetoidUtils.} Any type $A$ can be viewed as a setoid with propositional equality $\equiv$ as the equivalence relation.

@@

\paragraph*{Equiv.} Defines extensional equivalence of functions $\sim$ and shows that it is an equivalence relation. Defines equivalence between sets $\simeq$ using two functions that go back and forth and whose compositions are extensionally equivalent to the identity, and shows that this equivalence is indeed an equivalence relation. Finally shows that equivalences are injective.

@@

\paragraph*{CauchyEquiv.} Defines the Cauchy representation of
permutations as
$\texttt{Cauchy}~m~n = \texttt{Vec}~(\texttt{Fin}~m)~n$. The
representation is not tight at this point as it neither enforces that
$m=n$ nor that the elements of the vectors are a permutation of the
set $\{0,\ldots,n-1\}$. This is however a building block for actual
permutations (defined in \texttt{ConcretePermutation}) which enforce
both constraints. For that reason, the Cauchy representation has no
inverse and hence is not a commutative semiring unless one postulates
the following:
\[
\textbf{postulate}~\texttt{sym-iso}~:~\{m~n~:~\mathbb{N}\} \rightarrow
  \texttt{Cauchy}~m~n \rightarrow \texttt{Cauchy}~n~m
\]

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{?}

>>>>

\paragraph*{DivModUtils.} External library for reasoning about
uniqueness of \texttt{divMod}. This is used extensively to mediate
between $\texttt{Fin}~(m*n)$ and
$\texttt{Fin}~m \times \texttt{Fin}~n$.

@@

\paragraph*{SetoidUtils.} Any discrete type $A$ can be viewed as a
setoid with propositional equality $\equiv$ as the equivalence
relation.

@@

\paragraph*{Equiv.} Defines extensional equivalence of functions
$\sim$ and shows that it is an equivalence relation. Defines
equivalence between sets $\simeq$ using two functions that go back and
forth and whose compositions are extensionally equivalent to the
identity, and shows that this equivalence is indeed an equivalence
relation. Finally shows that equivalences are injective and form a
congruence that respects $\uplus$ and $\times$.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bimonoidal Categories}

\paragraph*{CauchyBimonoidal.} Defines the Cauchy representation of
permutations as
$\texttt{Cauchy}~m~n = \texttt{Vec}~(\texttt{Fin}~m)~n$. The
representation is not tight at this point as it neither enforces that
$m=n$ nor that the elements of the vectors are a permutation of the
set $\{0,\ldots,n-1\}$. This is however a building block for actual
permutations (defined in \texttt{ConcretePermutation}) which enforce
both constraints. For that reason, the Cauchy representation has no
inverse and hence is not a commutative semiring unless one postulates
the following:
\[
\textbf{postulate}~\texttt{sym-iso}~:~\{m~n~:~\mathbb{N}\} \rightarrow
  \texttt{Cauchy}~m~n \rightarrow \texttt{Cauchy}~n~m
\]
The Cauchy representation has more structure: it is almost a groupoid
again modulo two postulates asserting that \texttt{sym-iso} is really
a left and right inverse.

@@
